An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-25 poly-embed-journal/poly-embed-journal.tex
Another iteration

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}_\red}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter\simplex$.
\end{lemma}
\begin{proof}
	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter F'$ with constant derivative $d\in\reals^d$.
	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.

@@

\polyhedralrangegamma*
\begin{proof}
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter\simplex$.
	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter\simplex$.

	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \in \F_\Y$.
	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
	The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
	Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.

	Now for $p \not \in \inter{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
\end{proof}

@@

	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
	Consider that for all $z \in \Sc_L$, we have $z \in \inter{\Sc_L} \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.

@@

\begin{proposition}
	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
  \jessie{still a conjecture.}
  Take $\theta \in \N^L(\mathcal{Z})$.
  For all $p \in \theta$, we then have 
  \begin{align*}
  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
  &\iff p \in \Gamma_u~.~
  \end{align*}
  \jessie{Not quite... we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter{\Sc_L}$ or something similar for the first to second lines of equality.  Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.  i.e. we need Conjecture 1.
  }
  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
\end{proof}

@@

\begin{theorem}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.

	Now let $\Gamma := \Gamma[L]$.
	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.

@@

\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
  % Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H = \{H^+_{(w_1, b_1)}, \ldots, H^+_{(w_k, b_k)}\}$ such that $P = \cap \H$, and for all sets of closed halfspaces $\H'$ such that $P = \cap \H'$, we have $\H \subseteq \H'$.
  % Moreover, for each $i \in [k]$, letting $F_i := H_{(w_i, b_i)} \cap P$, the set of $\{F_1, \ldots, F_k\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
  \jessie{TODO}
\end{proof}
\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

\subsection{Phase 1: construct $\V^*$}
We will later consider losses over a finite set of outcomes $\Y$; for now, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.
Suppose we have a finite set $\V \subset \reals_+^\Y$.

\begin{definition}
  Define the function $g : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
  \end{align*}
  taking $g(0) = 0$.
\end{definition}
% Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

\begin{itemize}
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y$ analogously. 
\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.

@@

@@

\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
  $x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.

  or:
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{claim}
\begin{proof}
  $\implies$ 
  Fix any $c \in \reals$.
  $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
  As $y$ and $c$ were arbitrary, this shows the forward direction.

Some statements about facets and H-rep

@@

\begin{claim}\label{claim:G-unique-facets-Hstar}
  \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  % Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  % \jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
  %	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
  %	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
\end{proof}

@@

\begin{claim}\label{claim:g-gen-by-Vstar}
  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y)$
\end{claim}
\begin{proof}
  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
  Since $G$ is the hypograph of $g$, this means $g$ can be written as 
  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$. 
\end{proof}

\subsection{Projections to the positive orthant}

\begin{claim}\label{claim:vstar-supporting-G}
  For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
  \jessie{Notes in meeting:
    For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
    Argue $G \subseteq H^+_{v^*}$ by definition.
    Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}

  By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
  In particular, consider $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
  First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
  Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
  $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
  By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
  Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
\end{proof}

@@

\begin{claim}\label{claim:pi-preserves-dim}
  For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}

@@

  \jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI} just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis. 
  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$.  %, so we get $|\Y| + 1$ affinely independent vectors. 
  We claim $\{\pi(z_i)\}$ are affinely independent.
  Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
  Want to conclude $a_i = 0$ for all $i$.

  Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$ since $z_i \in F_v$, and therefore in $H_v$.
  So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.

  Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
  Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.

@@

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
  Let $x$, $v$.

  TFAE:

  $x \in \pi(F_v)$

  $(x,g(x)) \in F_v$

  $\inprod{v}{x}= g(x)$

  $v \in \argmin_{v' \in \V} \inprod{v'}{x}$
\end{lemma}
\begin{proof}
  \jessie{Don't like this in align environment}
  \begin{align*}
    x \in \pi(F_v)
    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in F_v\\
    &\iff \exists c \in \reals \text{ s.t. } (x,c) \in H_v \cap G\\
    & ...\\
    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
    &\iff (x,g(x)) \in F_v \\
    &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = \min_{v' \in \V} \inprod{v'}{x'}\} \\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
  \end{align*}
\end{proof}

>>>>

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
%\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\inter}{\mathrm{inter}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}_\red}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\begin{lemma}\label{lem:polyhedral-pd-same}
	Let $f_1,\ldots,f_m:\reals^d\to\reals$ be polyhedral convex functions.
	The power diagram induced by $\sum_{i=1}^m p_i f_i$ is the same for all $p \in \inter(\simplex)$.
\end{lemma}
\begin{proof}
	For any convex function $g$ with epigraph $P$, the proof of~\citet[Theorem 4]{aurenhammer1987power} shows that the power diagram induced by $g$ is determined by the facets of $P$.
	Let $F$ be a facet of $P$, and $F'$ its projection down to $\reals^d$.
	It follows that $g|_{F'}$ is affine, and thus $g$ is differentiable on $\inter(F')$ with constant derivative $d\in\reals^d$.
	Conversely, for any subgradient $d'$ of $g$, the set of points $\{x\in\reals^d : d'\in\partial g(x)\}$ is the projection of a face of $P$; we conclude that $F = \{(x,g(x))\in\reals^{d+1} : d\in\partial g(x)\}$ and $F' = \{x\in\reals^d : d\in\partial g(x)\}$.

@@

\polyhedralrangegamma*
\begin{proof}
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram $D_\Y$ induced by the projection of $P(p)$ onto $\reals^d$ is the same for any $p\in\inter(\simplex)$.
	Let $\F_\Y$ be the set of faces of $D_\Y$, which by the above are the set of faces of $P(p)$ projected onto $\reals^d$ for any $p\in\inter(\simplex)$.

	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \in \F_\Y$.
	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
	The optimality of $u$ is equivalent to $u'$ being contained in the face $F$ of $P(p)$ exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$.
	Thus, $\Gamma(p) = \argmin_{u\in\reals^d} \inprod{p}{L(u)}$ is a projection of $F$ onto $\reals^d$, which is an element of $\F_\Y$.

	Now for $p \not \in \inter(\simplex)$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
\end{proof}

@@

	Now, we want to show $\inf_{z' \in \Sc_L} \inprod{p}{z'} \geq \inf_{z' \in L(\reals^d)}\inprod{p}{z'}$.
	Consider that for all $z \in \Sc_L$, we have $z \in \inter(\Sc_L) \implies z \not \in \arginf_{z' \in \Sc_L}\inprod{p}{z'}$, where $\partial \Sc_L$ is the boundary of $\Sc_L$.
	Therefore, we have $\inf_{z' \in \Sc_L}\inprod{p}{z'} = \inf_{z' \in \partial\Sc_L}\inprod{p}{z'}$.

@@

\begin{proposition}
	Consider the loss $L:\reals^d \to \reals^n_+$ and $\Gamma := \prop{L}$ nondegenerate.
	Fix a finite set of $\{z_i\}_{i=1}^k$ so that each $z_i \in \Sc_L$ and $\cup_{z_i} \N^L(z_i) = \simplex$.
	Then $\N^L(\mathcal{Z}) = \{\N^L(z_i)\}_{i=1}^k = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
  \jessie{still a conjecture.}
  Take $\theta \in \N^L(\mathcal{Z})$.
  For all $p \in \theta$, we then have 
  \begin{align*}
  p \in \theta \iff \inprod{p}{z} &= \inf_{z' \in \Sc_L} \inprod{p}{z'}\\
  &= \inf_{z' \in L(\reals^d)} \inprod{p}{z'}\\
  &= \inf_{u \in \reals^d} \inprod{p}{L(u)}\\
  &= \inf_{u\in \reals^d} \E_p L(u, Y)\\
  &\iff p \in \Gamma_u~.~
  \end{align*}
  \jessie{Not quite... we have $\inf_{z' \in \Sc_L} \inprod{p}{z'} \leq \inf_{z' \in L(\reals^d)} \inprod{p}{z'}$, by $L(\reals^d) \subseteq \Sc_L$, but we need the fact that $\N^L(z) = \emptyset$ for all $z \in \inter(\Sc_L)$ or something similar for the first to second lines of equality.  Otherwise we just have $\Gamma_u \subseteq \N^L(z)$.  i.e. we need Conjecture 1.
  }
  Since this is true for all $p \in \theta$, we have $\theta = \Gamma_u$.
  As this is true for a finite set of $\mathcal{Z}$ whose positive normal sets union to the simplex, we have $\N^L(\mathcal{Z}) = \trim(\prop{L})$.
\end{proof}

@@

\begin{theorem}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter(\simplex)$.
	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.

	Now let $\Gamma := \Gamma[L]$.
	We claim for all $p\in\inter(\simplex)$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.

@@

%\raf{Let's use $\H^*$ for the minimum one, here and below; $\H$ for another one}
%\raf{Similarly $\V^*$ for the minimum one, below; $\V$ for another one}
\begin{theorem}\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, there is a unique finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, and for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
  Moreover, $\{H^+\cap P \mid H^+ \in \H^*\}$ is the set of facets of $P$.
\end{theorem}
\begin{proof}
  \jessie{TODO}
\end{proof}
\jessie{Need to find a good reference.  Cite a result for polytopes and transform the polyhedra into a polytope. Could state the result for class of polyhedra containing $G$.
  Add two facets and now it's a polytope.
}

\subsection{Phase 1: construct $\V^*$}
We will later consider losses over a finite set of outcomes $\Y$; to make notation consistent, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$ throughout, and let $d := |\Y|+1$.
Suppose we have a finite set $\V \subset \reals_+^\Y \times \reals$.

\begin{definition}
  Define the function $g : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
  \end{align*}
\end{definition}

We now introduce some of our notation.
\begin{itemize}
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y$ analogously. 
\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.

@@

\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
  $\cap \H_\Y = \reals^\Y_+ \times \reals$.
\end{claim}
\begin{proof}
  The result follows if we show $x \in \reals^\Y_+ \iff (x,c) \in \cap \H_\Y$ for all $c \in \reals$.

  $\implies$
  Fix any $c \in \reals$.
  $x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
  This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
  As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

We proceed with some observations about facets and dimension of the hypograph of $g$.

@@

\begin{claim}\label{claim:G-unique-facets-Hstar}
  \raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
  Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
\begin{proof}
  Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}

@@

\begin{claim}\label{claim:g-gen-by-Vstar}
  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y)$
\end{claim}
\begin{proof}
  $G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows from Corollary~\ref{cor-anything-gen-G-subset-Hstar}.
  Since $G$ is the hypograph of $g$, this means $g$ can be written as 
  $g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$. 
\end{proof}

\subsection{Projections to the positive orthant}
We now consider projections onto the positive orthant $\reals^\Y_+$.

\begin{claim}\label{claim:vstar-supporting-G}
  For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
% \jessie{Notes in meeting:
%   For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
%   Argue $G \subseteq H^+_{v^*}$ by definition.
%   Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}
%
  By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
  In particular, consider the normal $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
  First, $G \subseteq H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
  Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
  $H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
  By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
  Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
\end{proof}

@@

\begin{claim}\label{claim:pi-preserves-dim}
  For all $v\in\reals^\Y_+$, $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}

@@

  \jessie{Meeting notes: See \url{http://homepages.cae.wisc.edu/~linderot/classes/ie418/lecture11.pdf} for def of AI}
  \jessie{just need to argue that you never needed $c$ (i.e., $c$ was always just $g(x)$).  Maybe: take an affine basis, project, and show it's an affine basis.}
  As a reminder, we define the dimension of a polytope to be the dimension of its affine hull.
  Suppose we are given $|\Y|+1$ affinely independent vectors $z_i$ in $F_v$. 
  We claim their projections $\{\pi(z_i)\}$ are affinely independent.
  Let $a_1 + \ldots + a_{\Y+1} = 0$, such that $\sum_i a_i \pi(z_i) = 0$.
  Want to conclude $a_i = 0$ for all $i$, meaning they are affinely independent.

  Observe $z_i = (x_i, \inprod{v}{x_i})$ for all $i$; therefore, if $z_i \in F_v$ (e.g., $F_v$ supports $G$ at $x, \inprod{v}{x})$), then we also have $z_i \in H_v$.
  So $0 = \sum_i a_i \pi(z_i) = \sum_i a_i x_i$.
  Moreover, the sum $\sum_i a_i z_i = \sum_i a_i (x_i, \inprod{v}{x_i}) = (\sum_i a_i x_i, \inprod{v}{\sum_i a_i x_i}) = (0,0) = \vec 0$.
  Thus, since $a_i = 0$ for all $i$, the set $\{z_i\}$ is affinely independent and the dimensions of the affine hulls are therefore equal.
\end{proof}

@@

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
  Fix any $x \in \reals^\Y_+$.
  For any $v \in \V$, that the following are equivalent:

  (1) $(x,g(x)) \in F_v$

  (2) $\inprod{v}{x}= g(x)$

  (3) $v \in \argmin_{v' \in \V} \inprod{v'}{x}$

  (4) $x \in \pi(F_v)$
\end{lemma}
\begin{proof}
  \begin{align*}
    (x,g(x)) \in F_v
    &\iff (x,g(x)) \in \{(x',c) \in G \mid \inprod{v}{x'} = c\}\\
    &\iff  \inprod{v}{x} = g(x)\\
    &\iff \inprod{v}{x} = \min_{v' \in \V}\inprod{v'}{x}\\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
  \end{align*}
  This covers $1 \iff 2 \iff 3$.

  For $1 \iff 4$, the forward implication follows trivially by applying the definition of the projection $\pi$.
  For the reverse implication, consider some $x \in \pi(F_v)$.
  There must be a $c \in \reals$ so that $(x,c) \in F_v$.
  Expanding, this is actually saying $(x,c) \in \{(x',c') \in G \mid \inprod{v}{x'} = c\}$.
  In particular, this is true when $c = \inprod{v}{x}$, which defines a face of $G$ at $x$ if any only if $\inprod{v}{x} = g(x)$.
  Therefore, we have $(x, g(x)) \in F_v$.
\end{proof}
